\documentclass[10pt,landscape]{article}
\usepackage{multicol}
\usepackage{calc}
\usepackage{ifthen}
\usepackage[landscape]{geometry}
\usepackage[colorlinks = true, linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}

% To make this come out properly in landscape mode, do one of the following
% 1.
%  pdflatex latexsheet.tex
%
% 2.
%  latex latexsheet.tex
%  dvips -P pdf  -t landscape latexsheet.dvi
%  ps2pdf latexsheet.ps


% If you're reading this, be prepared for confusion.  Making this was
% a learning experience for me, and it shows.  Much of the placement
% was hacked in; if you make it better, let me know...


% 2008-04
% Changed page margin code to use the geometry package. Also added code for
% conditional page margins, depending on paper size. Thanks to Uwe Ziegenhagen
% for the suggestions.

% 2006-08
% Made changes based on suggestions from Gene Cooperman. <gene at ccs.neu.edu>

% 2012-11 - Stephen Skory
% Converted the latex cheat sheet to a yt cheat sheet, taken from
% http://www.stdout.org/~winston/latex/


% This sets page margins to .5 inch if using letter paper, and to 1cm
% if using A4 paper. (This probably isn't strictly necessary.)
% If using another size paper, use default 1cm margins.
\ifthenelse{\lengthtest { \paperwidth = 11in}}
	{ \geometry{top=.5in,left=.5in,right=.5in,bottom=0.85in} }
	{\ifthenelse{ \lengthtest{ \paperwidth = 297mm}}
		{\geometry{top=1cm,left=1cm,right=1cm,bottom=1cm} }
		{\geometry{top=1cm,left=1cm,right=1cm,bottom=1cm} }
	}

% Turn off header and footer
\pagestyle{empty}
 

% Redefine section commands to use less space
\makeatletter
\renewcommand{\section}{\@startsection{section}{1}{0mm}%
                                {-1ex plus -.5ex minus -.2ex}%
                                {0.5ex plus .2ex}%x
                                {\normalfont\large\bfseries}}
\renewcommand{\subsection}{\@startsection{subsection}{2}{0mm}%
                                {-1explus -.5ex minus -.2ex}%
                                {0.5ex plus .2ex}%
                                {\normalfont\normalsize\bfseries}}
\renewcommand{\subsubsection}{\@startsection{subsubsection}{3}{0mm}%
                                {-1ex plus -.5ex minus -.2ex}%
                                {1ex plus .2ex}%
                                {\normalfont\small\bfseries}}
\makeatother

% Define BibTeX command
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

% Don't print section numbers
\setcounter{secnumdepth}{0}


\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt plus 0.5ex}


% -----------------------------------------------------------------------

\begin{document}

\raggedright
\fontsize{3mm}{3mm}\selectfont
\begin{multicols}{3}


% multicol parameters
% These lengths are set only within the two main columns
%\setlength{\columnseprule}{0.25pt}
\setlength{\premulticols}{1pt}
\setlength{\postmulticols}{1pt}
\setlength{\multicolsep}{1pt}
\setlength{\columnsep}{2pt}

\begin{center}
     \Large{\textbf{yt Cheat Sheet}} \\
\end{center}

\subsection{General Info}
For everything yt please see \url{http://yt-project.org}.
Documentation \url{http://yt-project.org/doc/index.html}.
Need help? Start here \url{http://yt-project.org/doc/help/} and then
try the IRC chat room \url{http://yt-project.org/irc.html},
or the mailing list \url{http://lists.spacepope.org/listinfo.cgi/yt-users-spacepope.org}.
{\bf Installing yt:} The easiest way to install yt is to use the installation script
found on the yt homepage or the docs linked above.

\subsection{Command Line yt}
yt, and its convenience functions, are launched from a command line prompt.
Many commands have flags to control behavior.
Commands can be followed by
{\bf {-}{-}help} (e.g. {\bf yt render {-}{-}help}) for detailed help for that command
including a list of the available flags.

\texttt{iyt}\textemdash\ Load yt and IPython. \\
\texttt{yt load} {\it dataset}   \textemdash\ Load a single dataset.  \\
\texttt{yt help} \textemdash\ Print yt help information. \\
\texttt{yt stats} {\it dataset} \textemdash\ Print stats of a dataset. \\
\texttt{yt update} \textemdash\ Update yt to most recent version.\\
\texttt{yt update --all} \textemdash\ Update yt and dependencies to most recent version. \\
\texttt{yt instinfo} \textemdash\ yt installation information. \\
\texttt{yt notebook} \textemdash\ Run the IPython notebook server. \\
\texttt{yt serve} ({\it dataset}) \textemdash\  Run yt-specific web GUI ({\it dataset} is optional).\\
\texttt{yt upload\_image} {\it image.png} \textemdash\ Upload PNG image to imgur.com. \\
\texttt{yt upload\_notebook} {\it notebook.nb} \textemdash\ Upload IPython notebook to hub.yt-project.org.\\
\texttt{yt plot} {\it dataset} \textemdash\ Create a set of images.\\
\texttt{yt render} {\it dataset} \textemdash\ Create a simple
 volume rendering. \\
\texttt{yt mapserver} {\it dataset} \textemdash\ View a plot/projection in a Gmaps-like
 interface. \\
\texttt{yt pastebin} {\it text.out} \textemdash\ Post text to the pastebin at
 paste.yt-project.org. \\ 
\texttt{yt pastebin\_grab} {\it identifier} \textemdash\ Print content of pastebin to
 STDOUT. \\
 \texttt{yt hub\_register} \textemdash\ Register with
hub.yt-project.org. \\
\texttt{yt hub\_submit} \textemdash\ Submit hg repo to
hub.yt-project.org. \\
\texttt{yt bootstrap\_dev} \textemdash\ Bootstrap a yt 
development environment. \\
\texttt{yt bugreport} \textemdash\ Report a yt bug. \\
\texttt{yt hop} {\it dataset} \textemdash\  Run hop on a dataset. \\
\texttt{yt rpdb} \textemdash\ Connect to running rpd 
 session. 

\subsection{yt Imports}
In order to use yt, Python must load the relevant yt modules into memory.
The import commands are entered in the Python/IPython shell or
used as part of a script.
\newlength{\MyLen}
\settowidth{\MyLen}{\texttt{letterpaper}/\texttt{a4paper} \ }
\texttt{from yt.mods import \textasteriskcentered}  \textemdash\ 
Load base yt  modules. \\
\texttt{from yt.config import ytcfg}  \textemdash\ 
Used to set yt configuration options.
 If used, must be called before importing any other module.\\
\texttt{from yt.analysis\_modules.api import \textasteriskcentered}   \textemdash\ 
Load all yt analysis modules. \\
\texttt{from yt.analysis\_modules.\emph{halo\_finding}.api import \textasteriskcentered}  \textemdash\ 
Load halo finding modules. Other modules
are loaded in a similar way by swapping the 
{\em emphasized} text.
See the \textbf{Analysis Modules} section for a listing and short descriptions of each.

\subsection{Numpy Arrays}
Simulation data in yt is returned in Numpy arrays. The Numpy package provides a wealth of built-in
functions that operate on Numpy arrays. Here is a very brief list of some useful ones.
Please see \url{http://docs.scipy.org/doc/numpy/reference/} for the full
numpy documentation.\\
\settowidth{\MyLen}{\texttt{multicol} }
\texttt{v = a.max(), a.min()} \textemdash\ Return maximum, minimum of \texttt{a}. \\
\texttt{index = a.argmax(), a.argmin()} \textemdash\ Return index of max, 
min value of \texttt{a}.\\
\texttt{v = a[}{\it index}\texttt{]} \textemdash\ Select a single value from \texttt{a} at location {\it index}.\\
\texttt{b = a[}{\it i:j}\texttt{]} \textemdash\ Select the slice of values from \texttt{a} between
locations {\it i} to {\it j-1} saved to a new Numpy array \texttt{b} with length {\it j-i}. \\
\texttt{sel = (a > const)}  \textemdash\ Create a new boolean Numpy array \texttt{sel}, of the same shape as \texttt{a},
that marks which values of \texttt{a > const}. Other operators (e.g. \textless, !=, \%) work as well.\\
\texttt{b = a[sel]} \textemdash\ Create a new Numpy array \texttt{b} made up of elements from \texttt{a} that correspond to elements of \texttt{sel}
that are {\it True}. In the above example \texttt{b} would be all elements of \texttt{a} that are greater than \texttt{const}.\\
\texttt{a.dump({\it filename.dat})} \textemdash\ Save \texttt{a} to the binary file {\it filename.dat}.\\
\texttt{a = np.load({\it filename.dat})} \textemdash\ Load the contents of {\it filename.dat} into \texttt{a}.

\subsection{IPython Tips}
\settowidth{\MyLen}{\texttt{multicol} }
These tips work if IPython has been loaded, typically either by invoking
\texttt{iyt} or \texttt{yt load} on the command line, or using the IPython notebook (\texttt{yt notebook}).
\texttt{Tab complete} \textemdash\ IPython will attempt to auto-complete a
variable or function name when the \texttt{Tab} key is pressed, e.g. {\it HaloFi}\textendash\texttt{Tab} would auto-complete
to {\it HaloFinder}. This also works with imports, e.g. {\it from numpy.random.}\textendash\texttt{Tab}
would give you a list of random functions (note the trailing period before hitting \texttt{Tab}).\\
\texttt{?, ??} \textemdash\ Appending one or two question marks at the end of any object gives you
detailed information about it, e.g. {\it variable\_name}?.\\
Below a few IPython ``magics'' are listed, which are IPython-specific shortcut commands.\\
\texttt{\%paste} \textemdash\ Paste content from the system clipboard into the IPython shell.\\
\texttt{\%hist} \textemdash\ Print recent command history.\\
\texttt{\%quickref} \textemdash\ Print IPython quick reference.\\
\texttt{\%pdb} \textemdash\ Automatically enter the Python debugger at an exception.\\
\texttt{\%time, \%timeit} \textemdash\ Find running time of expressions for benchmarking.\\
\texttt{\%lsmagic} \textemdash\ List all available IPython magics. Hint: \texttt{?} works with magics.\\


Please see \url{http://ipython.org/documentation.html} for the full
IPython documentation.

\subsection{Load and Access Data}
The first step in using yt is to reference a simulation snapshot.
After that, simulation data is generally accessed in yt using {\it Data Containers} which are Python objects
that define a region of simulation space from which data should be selected.
\settowidth{\MyLen}{\texttt{multicol} }
\texttt{pf = load(}{\it dataset}\texttt{)} \textemdash\   Reference a single snapshot.\\
\texttt{dd = pf.h.all\_data()} \textemdash\ Select the entire volume.\\
\texttt{a = dd[}{\it field\_name}\texttt{]} \textemdash\ Saves the contents of {\it field} into the
numpy array \texttt{a}. Similarly for other data containers.\\
\texttt{pf.h.field\_list} \textemdash\ A list of available fields in the snapshot. \\
\texttt{pf.h.derived\_field\_list} \textemdash\ A list of available derived fields
in the snapshot. \\
\texttt{val, loc = pf.h.find\_max("Density")} \textemdash\ Find the \texttt{val}ue of
the maximum of the field \texttt{Density} and its \texttt{loc}ation. \\
\texttt{sp = pf.sphere(}{\it cen}\texttt{,}{\it radius}\texttt{)} \textemdash\   Create a spherical data 
container. {\it cen} may be a coordinate, or ``max'' which 
centers on the max density point. {\it radius} may be a float in 
code units or a tuple of ({\it length, unit}).\\

\texttt{re = pf.region({\it cen}, {\it left edge}, {\it right edge})} \textemdash\ Create a
rectilinear data container. {\it cen} is required but not used.
{\it left} and {\it right edge} are coordinate values that define the region.

\texttt{di = pf.disk({\it cen}, {\it normal}, {\it radius}, {\it height})} \textemdash\ 
Create a cylindrical data container centered at {\it cen} along the 
direction set by {\it normal},with total length
 2$\times${\it height} and with radius {\it radius}. \\
 
 \texttt{bl = pf.boolean({\it constructor})} \textemdash\ Create a boolean data
 container. {\it constructor} is a list of pre-defined non-boolean 
 data containers with nested boolean logic using the
 ``AND'', ``NOT'', or ``OR'' operators. E.g. {\it constructor=}
 {\it [sp, ``NOT'', (di, ``OR'', re)]} gives a volume defined
 by {\it sp} minus the patches covered by {\it di} and {\it re}.\\
 
\texttt{pf.h.save\_object(sp, {\it ``sp\_for\_later''})} \textemdash\ Save an object (\texttt{sp}) for later use.\\
\texttt{sp = pf.h.load\_object({\it ``sp\_for\_later''})} \textemdash\ Recover a saved object.\\


\subsection{Defining New Fields \& Quantities}
\texttt{yt} expects on-disk fields, fields generated on-demand and in-memory. Quantities reduce a field (e.g. "Density") defined over an object (e.g. "sphere") to get a single value (e.g. "Mass"). \\
\texttt{def \_MetalMassMsun({\it field},{\it data})}\\
\texttt{\hspace{4 mm} return data["Metallicity"]*data["CellMassMsun"]}\\
\texttt{add\_field("MetalMassMsun",function=\_MetalMassMsun)}\\
Define a new quantity; note the first function operates on grids and data objects and the second on the results of the first. \\
\texttt{def \_TotalMass(data): }\\
\texttt{\hspace{4 mm} baryon\_mass = data["CellMassMsun"].sum()}\\
\texttt{\hspace{4 mm} particle\_mass = data["ParticleMassMsun"].sum()}\\
\texttt{\hspace{4 mm} return baryon\_mass, particle\_mass}\\
\texttt{def \_combTotalMass(data, baryon\_mass, particle\_mass):}\\
\texttt{\hspace{4 mm} return baryon\_mass.sum() + particle\_mass.sum()}\\
\texttt{add\_quantity("TotalMass", function=\_TotalMass,}\\
\texttt{\hspace{4 mm} combine\_function=\_combTotalMass, n\_ret = 2)}\\



\subsection{Slices and Projections}
\settowidth{\MyLen}{\texttt{multicol} }
\texttt{slc = SlicePlot(pf, {\it axis}, {\it field}, {\it center=}, {\it width=}, {\it weight\_field=}, {\it additional parameters})} \textemdash\ Make a slice plot
perpendicular to {\it axis} of {\it field} weighted by {\it weight\_field} at (code-units) {\it center} with 
{\it width} in code units or a (value, unit) tuple. Hint: try {\it SlicePlot?} in IPython to see additional parameters.\\
\texttt{slc.save({\it file\_prefix})} \textemdash\ Save the slice to a png with name prefix {\it file\_prefix}.
\texttt{.save()} works similarly for the commands below.\\

\texttt{prj = ProjectionPlot(pf, {\it axis}, {\it field}, {\it addit. params})} \textemdash\ Make a projection. \\
\texttt{prj = OffAxisSlicePlot(pf, {\it normal}, {\it fields}, {\it center=}, {\it width=}, {\it depth=},{\it north\_vector=},{\it weight\_field=})} \textemdash Make an off-axis slice. Note this takes an array of fields. \\
\texttt{prj = OffAxisProjectionPlot(pf, {\it normal}, {\it fields}, {\it center=}, {\it width=}, {\it depth=},{\it north\_vector=},{\it weight\_field=})} \textemdash Make an off axis projection. Note this takes an array of fields. \\

\subsection{Plot Annotations}
\settowidth{\MyLen}{\texttt{multicol} }
Plot callbacks are functions itemized in a registry that is attached to every plot object. They can be accessed and then called like \texttt{ prj.annotate\_velocity(factor=16, normalize=False)}. Most callbacks also accept a {\it plot\_args} dict that is fed to matplotlib annotator. \\
\texttt{velocity({\it factor=},{\it scale=},{\it scale\_units=}, {\it normalize=})} \textemdash\ Uses field "x-velocity" to draw quivers\\
\texttt{magnetic\_field({\it factor=},{\it scale=},{\it scale\_units=}, {\it normalize=})} \textemdash\ Uses field "Bx" to draw quivers\\
\texttt{quiver({\it field\_x},{\it field\_y},{\it factor=},{\it scale=},{\it scale\_units=}, {\it normalize=})} \\
\texttt{contour({\it field=},{\it ncont=},{\it factor=},{\it clim=},{\it take\_log=}, {\it additional parameters})} \textemdash Plots a number of contours {\it ncont} to interpolate {\it field} optionally using {\it take\_log}, upper and lower {\it c}ontour{\it lim}its and {\it factor} number of points in the interpolation.\\
\texttt{grids({\it alpha=}, {\it draw\_ids=}, {\it periodic=}, {\it min\_level=}, {\it max\_level=})} \textemdash Add grid boundaries. \\
\texttt{streamlines({\it field\_x},{\it field\_y},{\it factor=},{\it density=})}\\
\texttt{clumps({\it clumplist})} \textemdash\ Generate {\it clumplist} using the clump finder and plot. \\
\texttt{arrow({\it pos}, {\it code\_size})} Add an arrow at a {\it pos}ition. \\
\texttt{point({\it pos}, {\it text})} \textemdash\ Add text at a {\it pos}ition. \\
\texttt{marker({\it pos}, {\it marker=})} \textemdash\ Add a matplotlib-defined marker at a {\it pos}ition. \\
\texttt{sphere({\it center}, {\it radius}, {\it text=})} \textemdash\ Draw a circle and append {\it text}.\\
\texttt{hop\_circles({\it hop\_output}, {\it max\_number=}, {\it annotate=}, {\it min\_size=}, {\it max\_size=}, {\it font\_size=}, {\it print\_halo\_size=}, {\it fixed\_radius=}, {\it min\_mass=}, {\it print\_halo\_mass=}, {\it width=})} \textemdash\ Draw a halo, printing it's ID, mass, clipping halos depending on number of particles ({\it size}) and optionally fixing the drawn circle radius to be constant for all halos.\\
\texttt{hop\_particles({\it hop\_output},{\it max\_number=},{\it p\_size=},\\
{\it min\_size},{\it alpha=})} \textemdash\ Draw particle positions for member halos with a certain number of pixels per particle.\\
\texttt{particles({\it width},{\it p\_size=},{\it col=}, {\it marker=}, {\it stride=}, {\it ptype=}, {\it stars\_only=}, {\it dm\_only=}, {\it minimum\_mass=}, {\it alpha=})}  \textemdash\  Draw particles of {\it p\_size} pixels in a slab of {\it width} with {\it col}or using a matplotlib {\it marker} plotting only every {\it stride} number of particles.\\
\texttt{title({\it text})}\\

\subsection{The $\sim$/.yt/ Directory}
\settowidth{\MyLen}{\texttt{multicol} }
yt will automatically check for configuration files in a special directory (\texttt{\$HOME/.yt/}) in the user's home directory.

The \texttt{config} file \textemdash\ Settings that control runtime behavior. \\
The \texttt{my\_plugins.py} file \textemdash\ Add functions, derived fields, constants, or other commonly-used Python code to yt.




\subsection{Analysis Modules}
\settowidth{\MyLen}{\texttt{multicol}}
The import name for each module is listed at the end of each description (see \textbf{yt Imports}).

\texttt{Absorption Spectrum} \textemdash\ (\texttt{absorption\_spectrum}). \\
\texttt{Clump Finder} \textemdash\ Find clumps defined by density thresholds (\texttt{level\_sets}). \\
\texttt{Coordinate Transformation} \textemdash\ (\texttt{coordinate\_transformation}). \\
\texttt{Halo Finding} \textemdash\ Locate halos of dark matter particles (\texttt{halo\_finding}). \\
\texttt{Halo Mass Function} \textemdash\ Find halo mass functions from data and from theory (\texttt{halo\_mass\_function}). \\
\texttt{Halo Profiling} \textemdash\ Profile and project multiple halos (\texttt{halo\_profiler}). \\
\texttt{Halo Merger Tree} \textemdash\ Create a database of halo mergers (\texttt{halo\_merger\_tree}). \\
\texttt{Light Cone Generator} \textemdash\ Stitch datasets together to perform analysis over cosmological volumes. \\
\texttt{Light Ray Generator} \textemdash\ Analyze the path of light rays.\\
\texttt{Radial Column Density} \textemdash\ Calculate column densities around a point (\texttt{radial\_column\_density}). \\
\texttt{Rockstar Halo Finding} \textemdash\ Locate halos of dark matter using the Rockstar halo finder (\texttt{halo\_finding.rockstar}). \\
\texttt{Star Particle Analysis} \textemdash\ Analyze star formation history and assemble spectra (\texttt{star\_analysis}). \\
\texttt{Sunrise Exporter} \textemdash\ Export data to the sunrise visualization format (\texttt{sunrise\_export}). \\
\texttt{Two Point Functions} \textemdash\ Two point correlations (\texttt{two\_point\_functions}). \\


\subsection{Parallel Analysis}
\settowidth{\MyLen}{\texttt{multicol}}
Nearly all of yt is parallelized using MPI.
The {\it mpi4py} package must be installed for parallelism in yt.
To install {\it pip install mpi4py} on the command line usually works.
Execute python in parallel similar to this:\\
{\it mpirun -n 12 python script.py --parallel}\\
This command may differ for each system on which you use yt;
please consult the system documentation for details on how to run parallel applications.

\texttt{from yt.pmods import *} \textemdash\ Load yt faster when in parallel.
This replaces the usual \texttt{from yt.mods import *}.\\
\texttt{parallel\_objects()} \textemdash\ A way to parallelize analysis over objects
(such as halos or clumps).\\


\subsection{Pre-Installed Versions}
\settowidth{\MyLen}{\texttt{multicol}}
yt is pre-installed on several supercomputer systems.

\textbf{NICS Kraken} \textemdash\ {\it module load yt} \\


\subsection{Mercurial}
\settowidth{\MyLen}{\texttt{multicol}}
Please see \url{http://mercurial.selenic.com/} for the full Mercurial documentation.

\texttt{hg clone https://bitbucket.org/yt\_analysis/yt} \textemdash\ Clone a copy of yt. \\
\texttt{hg status} \textemdash\ Files changed in working directory.\\
\texttt{hg diff} \textemdash\ Print diff of all changed files in working directory. \\
\texttt{hg diff -r{\it RevX} -r{\it RevY}} \textemdash\ Print diff of all changes between revision {\it RevX} and {\it RevY}.\\
\texttt{hg log} \textemdash\ History of changes.\\
\texttt{hg cat -r{\it RevX file}} \textemdash\ Print the contents of {\it file} from revision {\it RevX}.\\
\texttt{hg heads} \textemdash\ Print all the current heads. \\
\texttt{hg revert -r{\it RevX file}} \textemdash\ Revert {\it file} to revision {\it RevX}. On-disk changed version is
moved to {\it file.orig}. \\
\texttt{hg commit} \textemdash\ Commit changes to repository. \\
\texttt{hg push} \textemdash\ Push changes to default remote repository. \\
\texttt{hg pull} \textemdash\ Pull changes from default remote repository. \\
\texttt{hg serve} \textemdash\ Launch a webserver on the local machine to examine the repository in a web browser. \\

\subsection{FAQ}
\settowidth{\MyLen}{\texttt{multicol}}

\texttt{pf.field\_info[`field'].take\_log = False} \textemdash\ When plotting \texttt{field}, do not take log.
Must enter \texttt{pf.h} before this command. \\


%\rule{0.3\linewidth}{0.25pt}
%\scriptsize

% Can put some final stuff here like copyright etc...

\end{multicols}

\end{document}
